\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[left=3.00cm, right=3.00cm, top=3.00cm, bottom=3.00cm]{geometry}
\author{Pablo Gonzalez}
\title{Final project document for the Artificial Intelligence class}
\begin{document}
	\maketitle
	
	\section{Contents}
	
	This submission contains:
	\begin{itemize}
	
	\item *.java and *.bin: source and compiled files for all the classes used in the project. 
	
	Among them are:
	\begin{itemize} 
	\item An abstract class for problems (Problem) with its corresponding implementations for each problem 
	\begin{itemize}
	\item BananagramsProblem
	\item NPuzzleProblem
	\item MazeProblem
	\item HanoiProblem
	\end{itemize}
	\item An abstract class for search engines (SearchEngine) along with classes that extend it for each strategy
	\begin{itemize}
	\item BFS\_Engine
	\item DFS\_Engine
	\item Greedy\_Engine
	\item Astar\_Engine
	\item SMAstar\_Engine
	\end{itemize}
	\item The Node class to be used by all problems.
	
	
	\item Three runnable classes that perform different uses of the program
	\begin{itemize}
	\item Tester: a small program to test node generation and goal testing (see instructions below)
	\item SearchTester: Runs a specified kind of search on a preset version of the problem (see instructions below)
	\item RunExperiment\_Bananagrams: runs a larger experiment with several problems (specified in input files) 
	\end{itemize}
	\end{itemize}
	\item \lstinline!data/dictionary.txt!: a text file with the scrabble dictionary of all valid words to be used by the Bananagrams problem
	
	\item \lstinline!data/n-gramfreq.txt!: a series of text files with the collected frequencies of n-grams (for n between 2 and 15) as they appear in dictionary.txt
	\item \lstinline!data/ngramcounter.py!: the python code to generate the n-gram files
	\item\lstinline!data/problem/n-bananagramProblems!:files with the tilesets for randomly generated order n bananagrams problems highly probably to be solvable  
	\item \lstinline!data/bananagramgen.py!: the python code used to generate the problems
	
	\item \lstinline!Readme.pdf!: this file
	
	\end{itemize}
	
	\section{Running instructions}
	
	\subsection{Tester}
	To run the tester for node generation navigate to the containing directory within the terminal and run:
	
	\begin{lstlisting}
	$java Tester <problemnanme>
	
	\end{lstlisting}
	The \lstinline!<problemname>! variable can take four values, it chooses which problem to test, the allowed values are:
	\begin{lstlisting}
	Bananagrams
	Hanoi
	NPuzzle
	Maze
	\end{lstlisting}
	
	The response is printed to console standard output so it will appear in the terminal.
	If modifications are made the code will have to be recompiled for them to take effect, run:
	\begin{lstlisting}
	$javac Tester
	\end{lstlisting}
	The Rester program makes three tests and post the results:
	\begin{itemize}
	\item It first generates and prints all successors of the root node
	\item It then generates nodes at depths 2 through 4 (by taking always the first available action) and prints then
	\item It then takes a solution to the problem prints it and applies the goal test to it.
	\end{itemize}
	All tests worked as desired.
	
	\subsection{SearchTester}	
	To run the Search tester to do search on an instance of one of the problems navigate to the containing directory and type:
	
	\begin{lstlisting}
	$java SearchTester <problemnanme> <strategy> <extra args>
	\end{lstlisting}
	The \lstinline!<problemname>! argument can have the values:
	\begin{lstlisting}
	Bananagrams 
	Hanoi
	NPuzzle
	Maze
	\end{lstlisting}
	The \lstinline!<strategy>! argument can have the values:
	\begin{itemize}
	\item \lstinline!BFS!  	: Performs Breadth firs search
	\item\lstinline!DFS!	: Performs Depth fist search with depth cutoff
	\item \lstinline!Greedy!	: Performs Greedy Search
	\item \lstinline!Astar!	: Performs A* search
	\item \lstinline!SMA! 	: Performs simplified memory bound A* search
	\end{itemize}
	The extra arguments are only needed for 3 of the problems
	If \lstinline!<problemname>! is \lstinline!Bananagrams! then one extra argument with the order (an
	integer between 2 and 15) must be provided (please note that uninformed 
	search with orders bigger than 6 and heuristic search with orders larger
	than 10 will take a long time )
	
	If \lstinline!<problemname>! is Hanoi then the number of pegs followed by the number of
	disks should be provided.
	
	If \lstinline!<problemname>! is Npuzzle then an extra argument: 3, 8 or 15
	must be provided for the size of the puzzle.
	
	Some examples to run searches are
	\begin{lstlisting}
	$java SearchTester Bananagrams Astar 8
	
	$java SearchTester Hanoi Greedy 3 5
	
	$java SearchTester NPuzzle SMA 8
	\end{lstlisting}
	
	\subsection{RunExperiment\_Bananagrams}
	The third way to run an experiment is to use the RunExperiment\_Bananagrams, this
	will bulk run the problems stored in \lstinline!/problems! for a given order, it is run
	with the command:
	
	\begin{lstlisting}
	$java RunExperiment_Bananagrams <order>
	
	\end{lstlisting}
	Where \lstinline!<order>! is the size of the bananagrams you want to run
	

	
	
	The /results folder contains the ourput for runs of all problems from the search
	tester and from running the bananagrams bulk experiment for orders 4 and 5. 
	

	
	
\end{document}